---
title      : slidify_test
subtitle   : 
author     : Tyler Rinker
job        : 
logo       : 
biglogo    : 
license    : 
framework  : io2012
highlighter: highlight.js
hitheme    : tomorrow
mode       : selfcontained
widgets    : [mathjax, quiz, bootstrap]
---
```{r setup, include=FALSE}
# set global chunk options
opts_chunk$set(cache=FALSE)
opts_knit$set(message=FALSE)
options(gvis.plot.tag="chart")
packs <- c("reports", "slidify", "slidifyLibraries", "knitr", "knitcitations", 
    "googleVis")
lapply(packs, library, character.only = TRUE)
```

## Animation

	<div class="scianimator"><div id="Rplot" style="display: inline-block;"></div></div>
	<script src="js/Rplot.js"></script>
<!-- highlight R code -->
<script type="text/javascript">
	SyntaxHighlighter.autoloader(
	  "r    js/shBrushR.js"
	);
	SyntaxHighlighter.defaults["toolbar"] = false;
	SyntaxHighlighter.all();
</script>

--- 

## Animation (it can work)

I know this can work because I see it here:
http://mages.github.io/Introduction_to_googleVis/#18


---

## googleVis

```{r results="asis", echo=FALSE}
M <- gvisMotionChart(Fruits, "Fruit", "Year", options = list(width = 500, height = 350))
print(M, "chart")
```

---

## googleVis (it can work)

I once made slides using slidify and included a very similar animation, however I manually changed/added paths in the html file (I think) and can't even recreate it.  What is the proper way to add this animation (creating it time is a bad idea because there are so many images to create).

https://dl.dropboxusercontent.com/u/61803503/presentations/animation_test/test2.html#5.0

--- 

## session info

see: `session.info.txt`

```{r}
sink(file="session.info.txt")
sessionInfo()
sink()
```